%!TEX root = ../../controlbook.tex

%\begin{table}[ht!]
%\fcolorbox{realred}{none}%
%{\begin{minipage}{8.31cm}%
	

\par\noindent{\bf Examples (with solutions):}
\begin{multicols}{2}
\begin{description}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
	\item {\bf\controlbookhyperref{hw:arm_kinetic}{ A.2}} Kinetic energy.
	\item {\bf\controlbookhyperref{hw:arm_animation}{ A.a}} Simulink animation.	
	\item {\bf\controlbookhyperref{hw:arm_equations_of_motion}{ A.3}} Equations of Motion.
	\item {\bf\controlbookhyperref{hw:arm_s_function}{ A.b}} Simulink S-function.
	\item {\bf\controlbookhyperref{hw:arm_linearization}{ A.4}} Linearize equations of motion.
	\item {\bf\controlbookhyperref{hw:arm_transfer_function}{ A.5}} Transfer function model.
	\item {\bf\controlbookhyperref{hw:arm_state_space}{ A.6}} State space model.
	\item {\bf\controlbookhyperref{hw:arm_pd_pole_placement}{ A.7}} Pole placement using PD.
	\item {\bf\controlbookhyperref{hw:arm_PD_design}{ A.8}} Second order design.
	\item {\bf\controlbookhyperref{hw:arm_system_type}{ A.9}} Integrators and system type.
	\item {\bf\controlbookhyperref{hw:arm_root_locus}{ A.d}} Root locus.
	\item {\bf\controlbookhyperref{hw:arm_digital_PID}{ A.10}} Digital PID.
	\item {\bf\controlbookhyperref{hw:arm_state_feedback}{ A.11}} Full state feedback.
	\item {\bf\controlbookhyperref{hw:arm_integrator_state_feedback}{ A.12}} Full state with integrator.
	\item {\bf\controlbookhyperref{hw:arm_observer}{ A.13}} Observer based control.
	\item {\bf\controlbookhyperref{hw:arm_disturbance_observer}{ A.14}} Disturbance observer.
	\item {\bf\controlbookhyperref{hw:arm_bode}{ A.15}} Frequency Response.
	\item {\bf\controlbookhyperref{hw:arm_loopgain}{ A.16}} Loop gain.
	\item {\bf\controlbookhyperref{hw:arm_margins}{ A.17}} Stability margins.
	\item {\bf\controlbookhyperref{hw:arm_loopshaping}{ A.18}} Loopshaping design.
\end{description}
\end{multicols}

Note: The notation identifies the design configuration and the chapter
in which it is used: {\bf Example A.4} refers to the application of
approximations in Chapter~4 to linearize design
configuration~A\@. Similarly, {\bf Example A.a} refers to application
of Simulink in Appendix \underline{a} to design configuration~A.

%\end{minipage}}
%\end{table}