%!TEX root = ../../controlbook.tex

%\begin{table}[ht!]
%\fcolorbox{realred}{none}%
%{\begin{minipage}{8.31cm}%
%	

\par\noindent{\bf Examples (with solutions):}
\begin{multicols}{2}
\begin{description}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
	\item {\bf\controlbookhyperref{hw:satellite_kinetic}{C.2}} Kinetic energy.
	\item {\bf\controlbookhyperref{hw:satellite_animation}{C.a}} Simulink animation.
	\item {\bf\controlbookhyperref{hw:satellite_equations_of_motion}{C.3}} Equations of Motion.
	\item {\bf\controlbookhyperref{hw:satellite_s_function}{C.b}} Simulink S-function.
	\item {\bf\controlbookhyperref{hw:satellite_transfer_function}{C.4}} Equilibria.
	\item {\bf\controlbookhyperref{hw:satellite_transfer_function}{C.5}} Transfer function model.
	\item {\bf\controlbookhyperref{hw:satellite_state_space}{C.6}} State space model.
	\item {\bf\controlbookhyperref{hw:satellite_successive_loop_closure}{C.8}} Successive loop closure.
	\item {\bf\controlbookhyperref{hw:satellite_system_type}{C.9}} Integrators and system type.
	\item {\bf\controlbookhyperref{hw:satellite_root_locus}{C.d}} Root locus.
	\item {\bf\controlbookhyperref{hw:satellite_digital_PID}{C.10}} Digital PID.
	\item {\bf\controlbookhyperref{hw:satellite_state_feedback}{C.11}} Full state feedback.
	\item {\bf\controlbookhyperref{hw:satellite_integrator_state_feedback}{C.12}} Full state with integrator.
	\item {\bf\controlbookhyperref{hw:satellite_observer}{C.13}} Observer based control.
	\item {\bf\controlbookhyperref{hw:satellite_disturbance_observer}{C.14}} Disturbance observer.
	\item {\bf\controlbookhyperref{hw:satellite_bode}{C.15}} Frequency Response.
	\item {\bf\controlbookhyperref{hw:satellite_loopgain}{C.16}} Loop gain.
	\item {\bf\controlbookhyperref{hw:satellite_margins}{C.17}} Stability margins.
	\item {\bf\controlbookhyperref{hw:satellite_loopshaping}{C.18}} Loopshaping design.
\end{description}
\end{multicols}

%Note: The notation identifies the design configuration and the chapter
%in which it is used: {\bf Example C.4} refers to the application of
%approximations in Chapter~4 to linearize design
%configuration~C\@. Similarly, {\bf Example C.a} refers to application
%of Simulink in Appendix \underline{a} to design configuration~C.

%\end{minipage}}
%\end{table}