%!TEX root = ../../controlbook.tex

%\begin{table}[ht!]
%\fcolorbox{realred}{none}%
%{\begin{minipage}{8.31cm}%
	

\par\noindent{\bf Examples (with solutions):}
\begin{multicols}{2}
\begin{description}
\setlength{\itemsep}{0pt}
\setlength{\parskip}{0pt}
	\item {\bf\controlbookhyperref{hw:pendulum_kinetic}{B.2}} Kinetic energy.
	\item {\bf\controlbookhyperref{hw:pendulum_animation}{B.a}} Simulink animation.
	\item {\bf\controlbookhyperref{hw:pendulum_equations_of_motion}{B.3}} Equations of Motion.
	\item {\bf\controlbookhyperref{hw:pendulum_s_function}{B.b}} Simulink S-function.
	\item {\bf\controlbookhyperref{hw:pendulum_linearization}{B.4}} Linearize equations of motion.
	\item {\bf\controlbookhyperref{hw:pendulum_transfer_function}{B.5}} Transfer function model.
	\item {\bf\controlbookhyperref{hw:pendulum_state_space}{B.6}} State space model.
	\item {\bf\controlbookhyperref{hw:pendulum_successive_loop_closure}{B.8}} Successive loop closure.
	\item {\bf\controlbookhyperref{hw:pendulum_system_type}{B.9}} Integrators and system type.
	\item {\bf\controlbookhyperref{hw:pendulum_root_locus}{B.d}} Root locus.
	\item {\bf\controlbookhyperref{hw:pendulum_digital_PID}{B.10}} Digital PID.
	\item {\bf\controlbookhyperref{hw:pendulum_state_feedback}{B.11}} Full state feedback.
	\item {\bf\controlbookhyperref{hw:pendulum_integrator_state_feedback}{B.12}} Full state with integrator.
	\item {\bf\controlbookhyperref{hw:pendulum_observer}{B.13}} Observer based control.
	\item {\bf\controlbookhyperref{hw:pendulum_disturbance_observer}{B.14}} Disturbance observer.
	\item {\bf\controlbookhyperref{hw:pendulum_bode}{B.15}} Frequency Response.
	\item {\bf\controlbookhyperref{hw:pendulum_loopgain}{B.16}} Loop gain.
	\item {\bf\controlbookhyperref{hw:pendulum_margins}{B.17}} Stability margins.
	\item {\bf\controlbookhyperref{hw:pendulum_loopshaping}{B.18}} Loopshaping design.
\end{description}
\end{multicols}

Note: The notation identifies the design configuration and the chapter
in which it is used: {\bf Example B.4} refers to the application of
approximations in Chapter~4 to linearize design
configuration~B\@. Similarly, {\bf Example B.a} refers to application
of Simulink in Appendix \underline{a} to design configuration~B.

%\end{minipage}}
%\end{table}
