From HW~\ref{ds:satellite}.\ref{chap:transfer_function_models}, the transfer function model for the inner loop is given by
\[
\Theta(s)  = \frac{\frac{1}{J_s}}{s^2+\frac{b}{J_s}s+\frac{k}{J_s}}\tau(s).
\]
Rate damping is added by designing the control signal so that
\[
\tau(s) = -k_D\frac{s}{\sigma s+1}\Theta(s) + \tau'(s).
\]
Solving for $\Theta(s)$ in terms of $\tau'(s)$ gives
\[
\Theta(s)  = \frac{\sigma s + 1}{\sigma J_s s^3 + (\sigma b + J_s)s^2+(\sigma k + b + k_D)s + k}\tau'(s).
\]
Therefore, for the inner loop we will set
\[
P_{in} = \frac{\sigma s + 1}{\sigma J_s s^3 + (\sigma b + J_s)s^2+(\sigma k + b + k_D)s + k}.
\]
\fref{fig:hw_satellite_compensator_in_design_1} shows the Bode plot of the plant $P_{in}(s)$ together with the design specification on input tracking and noise attenuation.
%
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_in_design_1}
   	{The Bode plot for the inner loop plant in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, together with the design specification.}
   	{fig:hw_satellite_compensator_in_design_1}
The first step is to add a proportional gain to satisfy the tracking requirement.
\fref{fig:hw_satellite_compensator_in_design_2} shows the corresponding Bode plot for a proportional gain of $k_P=30$.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_in_design_2}
   	{The Bode plot for the inner loop plant in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, with proportional gain.}
   	{fig:hw_satellite_compensator_in_design_2}
Since the phase margin is over $PM=60$~degrees, we add a low pass filter.  
\fref{fig:hw_satellite_compensator_in_design_3} shows the loop gain with the addition of the low pass filter
\[
C_{LPF} = \frac{10}{s+10},
\]
which has a phase margin of $PM=69.8$~degrees, and satisfies the noise specification.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_in_design_3}
   	{The Bode plot for the inner loop system in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, with proportional gain and low pass filter.}
   	{fig:hw_satellite_compensator_in_design_3}
The resulting compensator is
\[
C_{in}(s) = 30\left(\frac{10}{s+10}\right).
\]
Notice that the DC-gain is not equal to one.
The closed loop response for the inner subsystem
\[
\frac{P_{in}C_{in}}{1+P_{in}C_{in}},
\] 
as well as the unit step response for the output and control signal are all show in \fref{fig:hw_satellite_compensator_in_design_4}.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_in_design_4}
   	{The closed loop bode response, the unit step response for the output, and the unit step response for the input of the inner loop design in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}.}
   	{fig:hw_satellite_compensator_in_design_4}
The Matlab code used to design the inner loop is shown below.
\begin{lstlisting}
Plant = P_in;

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Define Design Specifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%--- general tracking specification ---
% track signals below this frequency
omega_r = 10^-2; 
% tracking error below this value
gamma_r = 10^(-40/20);  
w = logspace(log10(omega_r)-2,log10(omega_r));
        
%--- noise specification ---
% attenuate noise above this frequency
omega_n = 2*10^1;  
% attenuate noise by this amount
gamma_n = 10^(-40/20);   
w = logspace(log10(omega_n),2+log10(omega_n));

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Control Design
  C = 1;
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% proportional control: 
%   change cross over frequency
     kp = 30;
     C = C*kp;
     
% low pass filter: 
%   decrease gain at high frequency (noise)
     p = 10;
     LPF = tf(p,[1,p]);
     C = C*LPF;
       
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Convert controller to state space equations 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
[num,den] = tfdata(C,'v');
[P.Ain_C,P.Bin_C,P.Cin_C,P.Din_C]=tf2ss(num,den);

C_in = C;
\end{lstlisting}


The transfer function model for the outer loop was derived in HW~\ref{ds:satellite}.\ref{chap:transfer_function_models} to be
\[
\Phi(s) = \frac{\frac{b}{J_p}s+\frac{k}{J_p}}{s^2+\frac{b}{J_p}s+\frac{k}{J_p}}\Theta^r(s).
\]
Rate damping is added by designing the control signal so that
\[
\Theta^r(s) = -k_D\frac{s}{\sigma s+1}\Phi(s) + \Theta^{r'}(s).
\]
Solving for $\Phi(s)$ in terms of $\Theta^{r'}(s)$ gives
\[
\Phi(s)  = \frac{\sigma b s^2 + (\sigma k + b)s + k}{\sigma J_p s^3 + (\sigma b + J_p + bk_D)s^2+(\sigma k + b + kk_D)s + k}\Theta^{r'}(s).
\]
The plant for the outer loop is therefore
\[
P_{out} =  \frac{\sigma s + 1}{\sigma J_s s^3 + (\sigma b + J_s)s^2+(\sigma k + b + k_D)s + k}\frac{P_{in}C_{in}}{1+P_{in}C_{in}}.
\]
\fref{fig:hw_satellite_compensator_out_design_1} shows the Bode plot for $P_{out}$ together with the design specification on rejecting input disturbances and attenuating the noise.  The requirement that steady state error to a step requires that the slope as $s\to 0$ is $-20$~dB/dec, and is not shown in \fref{fig:hw_satellite_compensator_out_design_1}.
%
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_out_design_1}
   	{The Bode plot for the outer loop plant in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, together with the design specification.}
   	{fig:hw_satellite_compensator_out_design_1}

The first step is to add an integrator to meet the steady state tracking requirement.  \fref{fig:hw_satellite_compensator_out_design_2} shows the loop gain after adding the integral control
\[
C_{int} = \frac{s+0.4}{s}.
\]
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_out_design_2}
   	{The Bode plot for the outer loop system in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, with integral control.}
   	{fig:hw_satellite_compensator_out_design_2}
It is clear from Figure~~\ref{fig:hw_satellite_compensator_out_design_2} that the input disturbance requirement is satisfied with a large buffer.  To reduce the bandwidth of the system, and to make it easier to satisfy the noise attenuation requirement, a proportional gain of $k_P=0.5$ is added to the compensator.  The result is shown in \fref{fig:hw_satellite_compensator_out_design_3}
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_out_design_3}
   	{The Bode plot for the outer loop system in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, with proportional and integral control.}
   	{fig:hw_satellite_compensator_out_design_3}
To meet the noise specification, the low pass filter
\[
C_{lpf} = \frac{3}{s+3}
\]
is added to the compensator, and the resulting loopgain is shown in \fref{fig:hw_satellite_compensator_out_design_4}.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_out_design_4}
   	{The Bode plot for the outer loop system in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}, with proportional gain, integral control, and a low pass  filter.}
   	{fig:hw_satellite_compensator_out_design_4}
Since the phase margin is $PM=56.9$~degrees, we consider the phase margin specification to be satisfied.
The resulting compensator is
\[
C_{out}(s) = 0.5\left(\frac{s+0.4}{s}\right)\left(\frac{3}{s+3}\right).
\]
The closed loop response for both the inner and outer loop systems, 
as well as the unit step response for the output and control signal of the outer loops are all show in \fref{fig:hw_satellite_compensator_out_design_5}, where the prefilter
\[
F(s) = \frac{0.8}{s+0.8}
\]
has been added to reduce the peaking in the closed loop response.
\controlbookfigurefullpage{0.7}
	{6_design_studies/figures/hw_satellite_compensator_out_design_5}
   	{The closed loop bode response, the unit step response for the output, and the unit step response for the input of the inner loop design in HW~\ref{ds:satellite}.\ref{chap:loopshaping_design}.}
   	{fig:hw_satellite_compensator_out_design_5}


The Matlab code used to design the outer loop is shown below.
\begin{lstlisting}
Plant = minreal(P_out*(P_in*C_in/(1+P_in*C_in)));

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Define Design Specifications
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%--- input disturbance specification ---
omega_din = 10^-2;  
gamma_din = 0.1;  
w = logspace(log10(omega_din)-2,log10(omega_din));
Pmag=bode(Plant,w);
for i=1:size(Pmag,3), Pmag_(i)=Pmag(1,1,i); end

%--- noise specification --- 
omega_n = 10^1;  
gamma_n = 10^(-80/20);   
w = logspace(log10(omega_n),2+log10(omega_n));
plot(w,20*log10(gamma_n)*ones(size(w)),'g')
        
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Control Design
  C = tf([1],[1]);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% integral control: 
  % frequency at which integral action ends
  k_I = .4; 
  Integrator = tf([1,k_I],[1,0]);
  C = C*Integrator;

% proportional control: 
%   change cross over frequency
     kp = .5;
     C = C*kp;

% low pass filter: 
%   decrease gain at high frequency (noise)
     p = 3;
     LPF = tf(p,[1,p]);
     C = C*LPF;

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Prefilter Design
  F = tf([1],[1]);
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% low pass filter
    p = 0.8;  % frequency to start the LPF
    LPF = tf(p, [1,p]);
    F = F*LPF;

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Convert controller to state space equations 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
C=minreal(C);
[num,den] = tfdata(C,'v');
[P.Aout_C,P.Bout_C,P.Cout_C,P.Dout_C]...
	=tf2ss(num,den);

[num,den] = tfdata(F,'v');
[P.Aout_F, P.Bout_F, P.Cout_F, P.Dout_F]...
	=tf2ss(num,den);

C_out=C;
\end{lstlisting}

See \controlbookurl{http://controlbook.byu.edu} for the complete solution.


